Network Configuration Synthesis with Abstract Topologies

### 2016-11-13 paper/abstraction/paper.tex
pass over abstract

\textbf{Abstract---}
\ryan{Copied from conclusion for reference}
We develop \sysname, the first system that can generate device configuration templates for large networks from high-level specifications of network topology and policy. \sysname is based on new abstractions for capturing parameterized network topologies, and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance. Our analysis operates entirely in the abstract domain and guarantees correctness for all concrete instantiations of the topology. Experiments with many types of real-world topologies and policies show that our abstractions and analysis are precise and that, for large networks, configuration synthesis is two orders of magnitude faster than systems that operate over concrete topologies.

>>>>

\textbf{Abstract---}
We develop \sysname, a system to generate provably-correct configurations for large, evolving networks from high-level specifications of their topology, routing policy, and fault-tolerance requirements. It is based on new abstractions for capturing parameterized network topologies, and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance. Our analysis operates entirely on abstract topologies and guarantees correctness for all concrete instantiations of the topology. Its output is also guaranteed to require minimal changes to the configurations of existing devices when the topology evolves to include new devices or links. Our experiments with many types of real-world topologies and policies show that our abstractions and fault-tolerance analysis are precise. They also show that, for large networks, our configuration synthesis is two orders of magnitude faster than systems that operate over concrete topologies.

%\ryan{Copied from conclusion for reference}
%We develop \sysname, the first system that can generate device configuration templates for large networks from high-level specifications of network topology and policy. \sysname is based on new abstractions for capturing parameterized network topologies, and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance. Our analysis operates entirely in the abstract domain and guarantees correctness for all concrete instantiations of the topology. Experiments with many types of real-world topologies and policies show that our abstractions and analysis are precise and that, for large networks, configuration synthesis is two orders of magnitude faster than systems that operate over concrete topologies.
